---
output: 
  pdf_document:
    latex_engine: xelatex
theme: tango
params:
  exam: 2
  year: 2018
  semester: Spring
  seed: 84322
  mcs: 15
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = "    ",
                      fig.height = 3,
                      fig.width = 5,
                      fig.align = 'center')
```

\Huge EDUC 6050 \normalsize  \hfill Name:___________________________

\large In-Class Exam `r params$exam` \normalsize (`r paste(params$semester, params$year)`) \hfill Score:________ /100

\vspace{10pt}

**Directions:** Complete all the questions. As the syllabus says you may use your "printed discussion points, homework, and other notes during examinations." Good luck!


```{r questions}
library(tidyverse)
library(furniture)
library(jmv)
library(here)
set.seed(params$seed)

capture_jmv <- function(output){
  out <- capture.output(output)
  out <- gsub("Independent|test|ANOVA|Samples|T-|Test|Correlation|Matrix", "", out)
  cat(paste(gsub("─", "-", out), "\n"))
}

code_chunks <- function(q,num){
  if (!is.na(q$Code)){
    cat("\\section{Question", num, "}")
    if (grepl("ggplot", q$Code)){
      eval(parse(text = q$Code)) %>% print()
      return()
    }
    cat('\n```\n')
    if (grepl("ttest", q$Code)){
        capture_jmv(eval(parse(text = q$Code))$ttest)
    } else if (grepl("anova", q$Code)){
        capture_jmv(eval(parse(text = q$Code))$main)
    } else if (grepl("cont", q$Code)){
        capture_jmv(eval(parse(text = q$Code))$freqs)
    } else if (grepl("corr", q$Code)){
        capture_jmv(eval(parse(text = q$Code))$matrix)
    }
    cat('\n```\n')
  }
}

formatMC <- function(q,qnum) {
  
  cat(qnum, '. ', q$Question, sep='')
  cat(' \n')
  cat(' \n')
  
  options <- c(q$CorrectAnswer,q$Lure1,q$Lure2,q$Lure3)
  randorder <- sample(4)
  cat('  \tA.',options[randorder[1]])
  cat('  \n')
  cat('  \tB.',options[randorder[2]])
  cat('  \n')
  cat('  \tC.',options[randorder[3]])
  cat('  \n')
  cat('  \tD.',options[randorder[4]])
  cat('  \n')
  optionLetters <- c('A','B','C','D')
  correct <- optionLetters[which(randorder==1)]
  correct
}

questions <- rio::import(here("Exams","questions2.xlsx"))
```

```{r selections}
## Select 15 MCs
num_mc <- params$mcs
questions <- questions %>% 
  mutate(keep = case_when(Unit == 2 ~ 1,
                          Unit == 1 & sample(c(TRUE, FALSE), sum(Unit == 1), .4) ~ 1,
                          TRUE ~ 0)) %>% 
  filter(keep == 1 | Unit == 2) %>% 
  filter(TakeHome == 0) %>% 
  filter(row_number() %in% sample(1:nrow(.), num_mc)) %>% 
  arrange(Unit)
```

```{r}
gss <- rio::import("https://cehs-research.github.io/EDUC-7610/GSS_Data/Data/GSS_reduced_example.csv") %>% 
  filter(row_number() %in% sample(1:nrow(.), 2000, replace = TRUE)) %>% 
  filter(educ < 50) %>% mutate(marital = case_when(marital == "Married" ~ "Married", 
                                                   TRUE ~ "Not Married"))
```

## Multiple Choice (5 pts each) {-}

```{r presentQuestions, echo=FALSE, results="asis"}
# Loop through questions
# presenting them in the appropriate format and storing the correct answers
print_questions <- function(questions){
  correct.all <- character(length=nrow(questions))
  order.all <- integer(length=nrow(questions))
  for (n in c(1:nrow(questions))) {
    cat('  \n')
    q <- questions[n,]
    correct <- formatMC(q,n)
    correct.all[n] <- correct
    order.all[n] <- n
  }
}
print_questions(questions)
```

## Interpretation (25 pts)

Let's say you are interested in understanding how watching The Office influence individuals' views of regarding awkward social interactions. You ask individuals how much they've watched The Office and present them with awkward social interactions (via video) to have them rate the awkwardness. You go through each step of the hypothesis test, you see no problems with the assumptions and have decided on an alpha of .05 for concluding significance. You decide to control for age and biological sex in the analysis. You assess the data and find the following results.

- What analysis did you use?

- What is the effect of watching The Office on the ratings of awkwardness?

- What does the $R^2$ mean here?

```{r, comment = "                                   "}
df <- tibble::tibble(
  office = runif(100, 0, 20),
  sex = rbinom(100, 1, .5),
  age = runif(100, 20, 69),
  awkwardness = -.2 * office + .07 * age + sex + 2*rnorm(100)
)

jmv::linReg(data = df, dep = awkwardness, covs = vars(office, age, sex),
            blocks = list(list('office', 'age', 'sex')))$modelFit %>% 
  capture_jmv()

jmv::linReg(data = df, dep = awkwardness, covs = vars(office, age, sex),
            blocks = list(list('office', 'age', 'sex')))$models %>% 
  capture_jmv()
```




\newpage

# Output Page

```{r presentOutput, echo=FALSE, results="asis"}
# Loop through questions
# presenting them in the appropriate format and storing the correct answers
print_output <- function(questions){
  correct.all <- character(length=nrow(questions))
  order.all <- integer(length=nrow(questions))
  for (n in c(1:nrow(questions))) {
    cat('  \n')
    q <- questions[n,]
    code_chunks(q,n)
    
    if (n == 6){
      cat("\\vspace{6pt}")
    }
    
  }
}
print_output(questions)
```


```{r finishUp, echo=FALSE, eval = FALSE}
questions$Key <- correct.all
questions$Order <- order.all
# Simplify the question key
questions %>%
  select(Order,Points,Question,CorrectAnswer,Key) -> questions.key
# Write out questions file with key included
write.csv(questions.key,file=paste0(questionsFile,"_withkey_v",seedNum,".csv"))
```
